\large{\bf Looking forwards and backwards through locally regulated populations }

### 2023-01-10 forwards-and-backwards.tex
.

\begin{proposition}[Line of descent construction]
    \label{prop:limiting_construction}
Let $\beta(x, \eta) = \meanq(x) + 2 \covq(x) \grad \log r(x, \eta)$
and $K(x)$ such that $\covq(x) = K(x) K(x)^T$.
Associate with each label $a \in \labelspace$
an independent $d$-dimensional Brownian motion $W_a$
and an independent Poisson process $R_a$ on $[0, \infty)^2$
with Lebesgue mean measure,
as before with points ordered in some way.
Given $\eta_0 \in \measures$,
let $(x_i, u_i)$ be the points of a Poisson process
with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta_0$ and Lebesgue measure.
For each point begin a line of descent
with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
Suppose that the spatial locations and level of each line of descent $a$
solve, for $\tau_a \le t < \sigma_a$ as,
where $\sigma_a = \lim_{K \to \infty} \inf\{t \ge 0: U_a(t) > K\}$,
as
\begin{align*}
X_a(t)
    &=
    X_a(\tau_a)
    + \int_{\tau_a}^{t}
        \beta(X_a(s), \eta(s)) ds
    + \int_{\tau_a}^{t}
        K(X_a(s)) dW_a(s)
    \\
U_a(t)
    &=
    U_a(\tau_a)
    + \int_{\tau_a}^{t}
    \bigg(
        \alpha \gamma(X_a(s),\eta(s))
        r(X_a(s), \eta(s)) U_a(s)^2
\\ &\qquad \qquad \qquad {}   
        -
        \left\{
            \gamma(X_a(s),\eta(s)) \DG r(X_a(s),\eta(s))
            + F(X_a(s), \eta(s))
        \right\}
        U_a(s)
    \bigg)
    ds .
\end{align*}
Each point in each $R_a$ denotes a potential birth time for $a$:
if the $j^\text{th}$ point in $R_a$ is $(t, v)$, with $\sigma_a \le t < \tau_a$,
then a new line of descent with label $a \concat j$ is produced,
with birth time $\tau_{a \concat j} = t$,
    location $X_{a \concat j}(t) = X_a(t)$, and level
$$
    U_{a \concat j}(t) = U_a(t)
    + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) } .
$$
For any solution to the equations above, the processes defined by
\begin{align*}
    \eta_t
    =
    \lim_{u_0 \to \infty} \frac{1}{u_0}
        \sum_{a : \tau_a \le t < \sigma_a \;\&\; U_a(t) < u_0} \delta_{X_a(t)}
    \qquad \text{and} \qquad
    \lp_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} 
\end{align*}
are solutions to the martingale problems of
Theorems~\ref{thm:nonlocal_convergence} and~\ref{thm:lookdown_convergence},
respectively.
\end{proposition}

In particular, note that if $\alpha=0$,
no new lines of descent are produced.
(More precisely, they are produced but ``at infinity'',
since the spatial motion of the line of descent is the result of production of these lineages.

>>>>

\begin{proposition}[Line of descent construction]
    \label{prop:limiting_construction}
Let $\beta(x, \eta) = \meanq(x) + 2 \covq(x) \grad \log r(x, \eta)$
and $K(x)$ such that $\covq(x) = K(x) K(x)^T$.
Associate with each label $a \in \labelspace$
an independent $d$-dimensional Brownian motion $W_a$
and an independent Poisson process $R_a$ on $[0, \infty)^2$
with Lebesgue mean measure,
as before with points ordered in some way.
Given $\eta_0 \in \measures$,
let $(x_i, u_i)$ be the points of a Poisson process
with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta_0$ and Lebesgue measure.
For each point begin a line of descent
with label $i$, location $X_i(0) = x_i$, level $U_i(0) = u_i$, and birth time $\tau_i = 0$.
Suppose that the spatial locations and level of each line of descent $a$
solve, for $\tau_a \le t < \sigma_a$ as,
where $\sigma_a = \lim_{K \to \infty} \inf\{t \ge 0: U_a(t) > K\}$,
as
\begin{align*}
X_a(t)
    &=
    X_a(\tau_a)
    + \int_{\tau_a}^{t}
        \beta(X_a(s), \eta_s) ds
    + \int_{\tau_a}^{t}
        K(X_a(s)) dW_a(s)
    \\
U_a(t)
    &=
    U_a(\tau_a)
    + \int_{\tau_a}^{t}
    \bigg(
        \alpha \gamma(X_a(s),\eta_s)
        r(X_a(s), \eta_s) U_a(s)^2
\\ &\qquad \qquad \qquad {}   
        -
        \left\{
            \gamma(X_a(s),\eta_s) \DG r(X_a(s),\eta_s)
            + F(X_a(s), \eta_s)
        \right\}
        U_a(s)
    \bigg)
    ds .
\end{align*}
Each point in each $R_a$ denotes a potential birth time for $a$:
if the $j^\text{th}$ point in $R_a$ is $(t, v)$, with $\sigma_a \le t < \tau_a$,
then a new line of descent with label $a \concat j$ is produced,
with birth time $\tau_{a \concat j} = t$,
    location $X_{a \concat j}(t) = X_a(t)$, and level
$$
    U_{a \concat j}(t) = U_a(t)
    + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) } ,
$$
if this is finite.
For any solution to the equations above, the processes defined by
\begin{align*}
    \eta_t
    =
    \lim_{u_0 \to \infty} \frac{1}{u_0}
        \sum_{a : \tau_a \le t < \sigma_a \;\&\; U_a(t) < u_0} \delta_{X_a(t)}
    \qquad \text{and} \qquad
    \lp_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} 
\end{align*}
are solutions to the martingale problems of
Theorems~\ref{thm:nonlocal_convergence} and~\ref{thm:lookdown_convergence},
respectively.
\end{proposition}

In particular, note that if $\alpha=0$,
no new lines of descent are produced.
(More precisely, they are produced but ``at infinity'',
since the spatial motion of the line of descent is the result of production of these lineages.)
